Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-03-23 notes/notes.tex
UNSTABLE STATE: COMPLETE REVERSE RG!

\documentclass{report}
\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix}
% \usepackage[draft]{graphicx}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.8in,top=0.3in,bottom=1.4in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{FiraSans} %% option 'sfdefault' activates Fira Sans as the default text font
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}

@@

\title{\bf Auxiliary Model Approach to Strongly-Correlated Systems}
\author{\Large Abhirup Mukherjee, Siddhartha Lal}
\date{\Large \today}

@@

The spectral function is plotted for three sets of values in fig.~\ref{spec_func}. For low values of \(U\), the profile is that of a single peak at zero frequency. This is expected because at the low energy effective theory, the high energy Hubbard side bands have been integrated out. As \(U\) increases, shoulder-like structures appear on either side of the peak, which finally, at larger \(U\), develop into two side-peaks. This is the microscopic theory, where high energy features are also relevant.
\begin{center}
	\includegraphics[width=0.8\textwidth]{../figures/gen_siam_spec_func.pdf}
	\captionof{figure}{Impurity spectral function for multiple values of \(U\). The increase in value of \(U\) is accompanied by the appearance of the side-peaks.}
	\label{spec_func}
\end{center}
The physics of the three peaks can now be looked into. Since the central peak is at zero energy, it has to do with excitations that do not cost any energy. There are two such excitations: excitations within the spin sector and within the charge sector.
\begin{equation}\begin{aligned}
	\ket{\uparrow} \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{J S_d^-}_{JS_d^+}}}\ket{\downarrow}, &&&&\ket{\Uparrow} \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{K C_d^-}_{K C_d^+}}}\ket{\Downarrow}\\
\end{aligned}\end{equation}
The thick arrow \(\Uparrow\) represents the charge isospin. At particle-hole symmetry, both the spin configurations has energy of \(\epsilon_d\), while the charge configurations have energy of \(2\epsilon_d + U=0\) and 0. Hence, no energy is required for these excitations, which is why see a macroscopic number of cloud electrons resonating with the impurity at the Fermi surface. Also note that if \(\hat S_i\) and \(\hat C_j\) are two operators of the spin and charge sector (\(i,j \in \left\{ x,y,z \right\} \)), then
\begin{equation}\begin{aligned}
	\hat S_i \hat C_j = \hat C_j \hat S_i = 0
\end{aligned}\end{equation}
We can see this by applying that operator on a basis state. Since the set of four states 
\begin{equation}\begin{aligned}
	\ket{\hat S_i = \pm \frac{1}{2}, \hat C_j = 0}, \ket{\hat S_i = 0, \hat C_j = \pm\frac{1}{2}}
\end{aligned}\end{equation}
are all independent, they form a basis. If we apply the operator on these states:
\begin{equation}\begin{aligned}
	\hat S_i \hat C_j \ket{\hat S_i} &= 0, &&&&\hat C_j \hat S_i \ket{S_i} = S_i \hat C_j \ket{S_i} = 0\\
	\hat C_j \hat S_i \ket{C_j} &= 0, &&&&\hat S_i \hat C_j \ket{\hat C_j} = C_j \hat S_i \ket{\hat C_j} = 0 \\
\end{aligned}\end{equation}
This shows that each operator acts only on its own subspace. \(S_i\) does not act on the charge sector, and vice-versa. There is no single-particle excitation here.

@@

\begin{figure}[!htb]
\centering
	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=4.000.pdf}
	\caption{Evolution of the zero-bandwidth ground state across the transition.}
\end{figure}

>>>>

\documentclass{report}
\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk}
% \usepackage[draft]{graphicx}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.8in,top=0.3in,bottom=1.4in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{FiraSans}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}

@@

\title{Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems}
\author{Abhirup Mukherjee, Siddhartha Lal}
\affil{Indian Institute of Science Education and Research Kolkata, Mohanpur}
\date{\today}

@@

The spectral function is plotted for three sets of values in fig.~\ref{spec_func}. For low values of \(U\), the profile is that of a single peak at zero frequency. This is expected because at the low energy effective theory, the high energy Hubbard side bands have been integrated out. As \(U\) increases, shoulder-like structures appear on either side of the peak, which finally, at larger \(U\), develop into two side-peaks. This is the microscopic theory, where high energy features are also relevant.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=0.00.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=3.00.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=5.00.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=10.00.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=25.00.pdf}
	\caption{Impurity spectral function for multiple values of \(U\). The increase in value of \(U\) is accompanied by the appearance of the side-peaks.}
	\label{spec_func}
\end{figure}
The physics of the three peaks can now be looked into. Since the central peak is at zero energy, it has to do with excitations that do not cost any energy. There are two such excitations: excitations within the spin sector and within the charge sector.
\begin{equation}\begin{aligned}
	\ket{\uparrow} \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{J S_d^-}_{JS_d^+}}}\ket{\downarrow}, &&&&\ket{\Uparrow} \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{K C_d^-}_{K C_d^+}}}\ket{\Downarrow}\\
\end{aligned}\end{equation}
The thick arrow \(\Uparrow\) represents the charge isospin. At particle-hole symmetry, both the spin configurations has energy of \(\epsilon_d\), while the charge configurations have energy of \(2\epsilon_d + U=0\) and 0. Hence, no energy is required for these excitations, which is why see a macroscopic number of cloud electrons resonating with the impurity at the Fermi surface. Also note that if \(\hat S_i\) and \(\hat C_j\) are two operators of the spin and charge sector (\(i,j \in \left\{ x,y,z \right\} \)), then
\begin{equation}\begin{aligned}
	\hat S_i \hat C_j = \hat C_j \hat S_i = 0
\end{aligned}\end{equation}
We can see this by applying that operator on a basis state. Since the set of four states 
\begin{equation}\begin{aligned}
	\ket{\hat S_i = \pm \frac{1}{2}, \hat C_j = 0}, \ket{\hat S_i = 0, \hat C_j = \pm\frac{1}{2}}
\end{aligned}\end{equation}
are all independent, they form a basis. If we apply the operator on these states:
\begin{equation}\begin{aligned}
	\hat S_i \hat C_j \ket{\hat S_i} &= 0, &&&&\hat C_j \hat S_i \ket{S_i} = S_i \hat C_j \ket{S_i} = 0\\
	\hat C_j \hat S_i \ket{C_j} &= 0, &&&&\hat S_i \hat C_j \ket{\hat C_j} = C_j \hat S_i \ket{\hat C_j} = 0 \\
\end{aligned}\end{equation}
This shows that each operator acts only on its own subspace. \(S_i\) does not act on the charge sector, and vice-versa. There is no single-particle excitation here.

@@

\begin{figure}[!htb]
\centering
	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=10.000.pdf}
	\caption{Evolution of the zero-bandwidth ground state across the transition.}
\end{figure}
